Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2020-11-10 manuscript.rmd
Printe references where needed

# References

@@

```{r hydro-calib, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "80%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-hydro-calib}")}
knitr::include_graphics(file.path("figures/hydro-calib2.jpeg"))
```

>>>>

# References
<div id="refs"></div>

@@

```{r hydro-calib, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "80%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-hydro-calib}")}
knitr::include_graphics(file.path("figures/2019-10-14_5000/best-fits/hydro-calib2.jpeg"))
```
